Analysis of Retrospective COVID-19 data

### 2020-10-09 manuscript/analysis_brms.Rmd
run more sensitivity analysis

@@

@@

@@

>>>>

```{r}
# all patients for which we have data for at least 7 days
data$surv_data_7 <- data$surv_data_last_day %>%
  filter(!(day < 7 & outcome3 == "Hospitalized"))

# all patients for which we have data for at least 7 days
data$surv_data_28 <- data$surv_data_last_day %>%
  filter(!(day < 28 & outcome3 == "Hospitalized"))
```

@@

### Basic binary model (7 days)

```{r, results="hide"}
fit_survival_base_7 <- brm(
  formula = form_survival_base,
  data = data$surv_data_7,
  prior = prior_survival_base,
  file = "models/fit_survival_base_7"
)
fit_survival_base_7 <- add_criterion(fit_survival_base_7, "loo")
```

```{r}
summary(fit_survival_base_7)
# ce <- conditional_effects(fit_survival_base_7)
# plot(ce, ask = FALSE)
```

```{r}
draws <- tidy_draws(fit_survival_base_7)
hypothesis_res_list[["hcq_az_survival_base_7"]] <- rbind(
  bayesian_hypothesis_res_from_draws(
    draws = draws$b_ever_hcqTRUE,
    model = "brms_binary_7",
    estimand = "logit(survival)",
    hypothesis = hypotheses$hcq_reduces_death,
    adjusted = "az, sex, age_norm, smoking, BMI"
  ),
  bayesian_hypothesis_res_from_draws(
    draws = draws$b_ever_azTRUE,
    model = "brms_binary_7",
    estimand = "logit(survival)",
    hypothesis = hypotheses$az_reduces_death,
    adjusted = "hcq, sex, age_norm, smoking, BMI"
  )
)
```

### Basic binary model (28 days)

```{r, results="hide"}
fit_survival_base_28 <- brm(
  formula = form_survival_base,
  data = data$surv_data_28,
  prior = prior_survival_base,
  file = "models/fit_survival_base_28"
)
fit_survival_base_28 <- add_criterion(fit_survival_base_28, "loo")
```

```{r}
summary(fit_survival_base_28)
# ce <- conditional_effects(fit_survival_base_28)
# plot(ce, ask = FALSE)
```

```{r}
draws <- tidy_draws(fit_survival_base_28)
hypothesis_res_list[["hcq_az_survival_base_28"]] <- rbind(
  bayesian_hypothesis_res_from_draws(
    draws = draws$b_ever_hcqTRUE,
    model = "brms_binary_28",
    estimand = "logit(survival)",
    hypothesis = hypotheses$hcq_reduces_death,
    adjusted = "az, sex, age_norm, smoking, BMI"
  ),
  bayesian_hypothesis_res_from_draws(
    draws = draws$b_ever_azTRUE,
    model = "brms_binary_28",
    estimand = "logit(survival)",
    hypothesis = hypotheses$az_reduces_death,
    adjusted = "hcq, sex, age_norm, smoking, BMI"
  )
)
```

@@

### Basic binary model (7 Days)

```{r, results="hide"}
fit_discharged_base_7 <- brm(
  formula = form_discharged_base,
  data = data$surv_data_7,
  prior = prior_discharged_base,
  file = "models/fit_discharged_base_7"
)
fit_discharged_base_7 <- add_criterion(fit_discharged_base_7, "loo")
```

```{r}
summary(fit_discharged_base_7)
# ce <- conditional_effects(fit_discharged_base_7)
# plot(ce, ask = FALSE)
```

```{r}
draws <- tidy_draws(fit_discharged_base_7)
hypothesis_res_list[["hcq_az_discharged_base_7"]] <- rbind(
  bayesian_hypothesis_res_from_draws(
    draws = draws$b_ever_hcqTRUE,
    model = "brms_binary_7",
    estimand = "logit(discharged)",
    hypothesis = hypotheses$hcq_increases_discharged,
    adjusted = "az, sex, age_norm, smoking, BMI"
  ),
  bayesian_hypothesis_res_from_draws(
    draws = draws$b_ever_azTRUE,
    model = "brms_binary_7",
    estimand = "logit(discharged)",
    hypothesis = hypotheses$az_increases_discharged,
    adjusted = "hcq, sex, age_norm, smoking, BMI"
  )
)
```

### Basic binary model (28 Days)

```{r, results="hide"}
fit_discharged_base_28 <- brm(
  formula = form_discharged_base,
  data = data$surv_data_28,
  prior = prior_discharged_base,
  file = "models/fit_discharged_base_28"
)
fit_discharged_base_28 <- add_criterion(fit_discharged_base_28, "loo")
```

```{r}
summary(fit_discharged_base_28)
# ce <- conditional_effects(fit_discharged_base_28)
# plot(ce, ask = FALSE)
```

```{r}
draws <- tidy_draws(fit_discharged_base_28)
hypothesis_res_list[["hcq_az_discharged_base_28"]] <- rbind(
  bayesian_hypothesis_res_from_draws(
    draws = draws$b_ever_hcqTRUE,
    model = "brms_binary_28",
    estimand = "logit(discharged)",
    hypothesis = hypotheses$hcq_increases_discharged,
    adjusted = "az, sex, age_norm, smoking, BMI"
  ),
  bayesian_hypothesis_res_from_draws(
    draws = draws$b_ever_azTRUE,
    model = "brms_binary_28",
    estimand = "logit(discharged)",
    hypothesis = hypotheses$az_increases_discharged,
    adjusted = "hcq, sex, age_norm, smoking, BMI"
  )
)
```

@@

### Basic Categorical model (7 Days)

```{r, results="hide"}
fit_outcome_base_7 <- brm(
  formula = form_outcome_base,
  data = data$surv_data_7,
  prior = prior_outcome_base,
  file = "models/fit_outcome_base_7"
)
fit_outcome_base_7 <- add_criterion(fit_outcome_base_7, "loo")
```

```{r}
summary(fit_outcome_base_7)
# ce <- conditional_effects(fit_outcome_base_7)
# plot(ce, ask = FALSE)
```

```{r}
draws <- tidy_draws(fit_outcome_base_7)
hypothesis_res_list[["hcq_az_outcome_base_7"]] <- rbind(
  bayesian_hypothesis_res_from_draws(
    draws = draws$b_muDeath_ever_hcqTRUE,
    model = "brms_categorical_7",
    estimand = "logit(death)",
    hypothesis = hypotheses$hcq_reduces_death,
    adjusted = "az, sex, age_norm, smoking, BMI"
  ),
  bayesian_hypothesis_res_from_draws(
    draws = draws$b_muDeath_ever_azTRUE,
    model = "brms_categorical_7",
    estimand = "logit(death)",
    hypothesis = hypotheses$az_reduces_death,
    adjusted = "hcq, sex, age_norm, smoking, BMI"
  ),
  bayesian_hypothesis_res_from_draws(
    draws = draws$b_muDischarged_ever_hcqTRUE,
    model = "brms_categorical_7",
    estimand = "logit(discharged)",
    hypothesis = hypotheses$hcq_increases_discharged,
    adjusted = "az, sex, age_norm, smoking, BMI"
  ),
  bayesian_hypothesis_res_from_draws(
    draws = draws$b_muDischarged_ever_azTRUE,
    model = "brms_categorical_7",
    estimand = "logit(discharged)",
    hypothesis = hypotheses$az_increases_discharged,
    adjusted = "hcq, sex, age_norm, smoking, BMI"
  )
)
```

### Basic Categorical model (28 Days)

```{r, results="hide"}
fit_outcome_base_28 <- brm(
  formula = form_outcome_base,
  data = data$surv_data_28,
  prior = prior_outcome_base,
  file = "models/fit_outcome_base_28"
)
fit_outcome_bas_28 <- add_criterion(fit_outcome_base_28, "loo")
```

```{r}
summary(fit_outcome_base_28)
# ce <- conditional_effects(fit_outcome_base_28)
# plot(ce, ask = FALSE)
```

```{r}
draws <- tidy_draws(fit_outcome_base_28)
hypothesis_res_list[["hcq_az_outcome_base_28"]] <- rbind(
  bayesian_hypothesis_res_from_draws(
    draws = draws$b_muDeath_ever_hcqTRUE,
    model = "brms_categorical_28",
    estimand = "logit(death)",
    hypothesis = hypotheses$hcq_reduces_death,
    adjusted = "az, sex, age_norm, smoking, BMI"
  ),
  bayesian_hypothesis_res_from_draws(
    draws = draws$b_muDeath_ever_azTRUE,
    model = "brms_categorical_28",
    estimand = "logit(death)",
    hypothesis = hypotheses$az_reduces_death,
    adjusted = "hcq, sex, age_norm, smoking, BMI"
  ),
  bayesian_hypothesis_res_from_draws(
    draws = draws$b_muDischarged_ever_hcqTRUE,
    model = "brms_categorical_28",
    estimand = "logit(discharged)",
    hypothesis = hypotheses$hcq_increases_discharged,
    adjusted = "az, sex, age_norm, smoking, BMI"
  ),
  bayesian_hypothesis_res_from_draws(
    draws = draws$b_muDischarged_ever_azTRUE,
    model = "brms_categorical_28",
    estimand = "logit(discharged)",
    hypothesis = hypotheses$az_increases_discharged,
    adjusted = "hcq, sex, age_norm, smoking, BMI"
  )
)
```
